Common sense approaches to sharing tabular data alongside publication

### 2021-09-14 new-paper.Rmd
work on addressing R2-2

The steps leading up to requiring data sharing are still vague and disincentivized. In comparison, although few journals require that code be submitted with publications, such a norm is more likely to be adopted if a foundation like the one we have described is established, with carrots rather than sticks. We have taught researchers how to write modular code via popular training initiatives such as The Carpentries. Commercial services like GitHub have made code sharing fun and productive. For more advanced researchers, data science languages have made it easier to package and disseminate code as reusable software. If we now require mandatory code sharing, it is quite likely that more of it will be useful than the data currently being shared.

>>>>

The steps leading up to requiring data sharing are still vague and disincentivized. In comparison, although few journals require that code be submitted with publications, such a norm is more likely to be adopted if a foundation like the one we have described is established, with carrots rather than sticks. We have taught researchers how to write modular code via popular training initiatives such as The Carpentries. Commercial services like GitHub have made code sharing fun and productive. For more advanced researchers, data science languages have made it easier to package and disseminate code as reusable software. If we now require mandatory code sharing, it is quite likely that more of it will be useful than the data currently being shared. Researchers will need to be familiar with existing tools and approaches for sharing data. There might be potential for researchers to reinvent the wheel, for example by creating new platforms for data sharing, when services such as zenodo and Dryad already exist. So it is worth mentioning that researchers should not reinvent new tools without an exhaustive search.
